\documentclass{article}
\usepackage{xcolor}

% Preamble
\title{Documatation Of this Web App}
\author{To-Do List}
\date{\today}

% Document Content
\begin{document}
\maketitle

\section{Introduction}
Welcome to our To-Do List Web App -This app simplifies your daily routine by allowing you to create, organize, and track your tasks efficiently. Add tasks, mark them as completed, and enjoy a clutter-free to-do list that keeps you focused on what truly matters. It's time to boost your productivity and regain control of your day with our intuitive and user-friendly app.
\section{$**$ How the To-Do List App Works $**$}
Our To-Do List App is designed to streamline your task management process. It operates on a simple and user-friendly principle:
\subsection{Add Tasks}
When you have a new task or to-do item, you can easily \textbf{\textcolor{blue}{add}} and  it to your list.

\subsection{$**$ Mark as Completed: $**$ }
As you work through your tasks, mark them as completed with a simple click or tap. Completed tasks are visually distinguished, making it easy to see what's left to do.

\subsection{$**$ Remove Completed Tasks:$**$ }
Once you've finished a task, you can remove it from your list. The app provides a convenient way to declutter your to-do list and focus on what's pending.

\subsection{$**$ Access Anywhere $**$ }
You can access your to-do list from any device with an internet connection, making it convenient to manage your tasks on the go.
\paragraph{Start using our app today, and experience the simplicity of task management at its best.}


\end{document}
